---
title       : Predict Car's Miles per Gallon (MPG) from Weight
subtitle    : A Simple Shiny App
author      : Luong The Vinh
job         : Manager, Business Analytics
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

`r opts_chunk$set(echo = FALSE)`

## Background: 1974 Motor Trend dataset
Data on fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models), e.g.:
``` {r}
head(mtcars)
```

---

## A Car's MPG Is Predominantly Determined by Its Weight
Result from simple linear regression model of MPG on Weight:
``` {r}
model <- lm(mpg ~ wt, mtcars)
model
```
* In terms of Adjusted R Squared, Weight explains **`r summary(model)$adj.r.squared`** (i.e. almost 3/4) of the variation in MPG

* In terms of P-value, Weight is statistically highly significant

---

## Shiny App: Predictive Model of MPG according to Weight
``` {r fig.width=9, fig.height=6}
illusWeight <- 3.3
dataFrame <- as.data.frame(illusWeight)
names(dataFrame) <- 'wt'
predMPG <- predict(model, dataFrame)
            
plot(mpg ~ wt, mtcars, col = 'blue')
title('MPG as an approximate linear function of Weight')
abline(model, col = 'red', lwd = 3)
abline(v = illusWeight)
abline(h = predMPG)
```

---

## Shiny App: Link & How-to-Use

* Go to weblink: https://luongthevinh.shinyapps.io/predictMPG/

* Simply specify your car's weight using the input slider, and see the interactive graph show the predicted MPG

* Have FUN!!!